Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-01 journal-draft/bare_jrnl_comsoc.tex
message compelxity

\begin{center}
\begin{table*}[!htb]
\caption{Signalling overhead}\label{tab_overhead}
{\renewcommand{\arraystretch}{1.15} %<- modify value to suit your needs
{\small
\hfill{}
\begin{threeparttable}
\begin{tabular}{|C{2 cm}|C{2.8 cm}|C{3.15 cm}|C{7.7 cm}|}
\hline
 Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
 ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability on all cluster members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
 ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
 SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members ($|C(i)| |\mathcal{K}|$ bytes)
 \\ \hline
 Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) \cite{Efficient_broadcasting_gathering_adhoc}		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
\end{tabular}
    \begin{tablenotes}
      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of $\{i, C\}, i\in C, i\in \mathcal{N}$.
    \end{tablenotes}
    \end{threeparttable}
}
}
\hfill{}
\end{table*}
\end{center}

>>>>

\begin{center}
\begin{table*}[!htb]
\caption{Signalling overhead}\label{tab_overhead}
{\renewcommand{\arraystretch}{1.15} %<- modify value to suit your needs
{\small
\hfill{}
\begin{threeparttable}
\begin{tabular}{|C{2 cm}|C{2.8 cm}|C{3.15 cm}|C{7.7 cm}|}
\hline
 Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content and size of the message 									\\ \hline
 ROSS-DGA, ROSS-$\delta$-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $N+n^2m$ (upper bound)  				&   \multirow{2}{*}{\parbox{7.7cm}{PhaseI: ID, $d_i$,$g_i$, which are 3 bytes;\\ PhaseII: Cluster head $i$ broadcasts channel availability on all cluster members, where are $|C(i)| |\mathcal{K}|$ bytes}}								\\ \cline{1-3}
 ROSS-DFA, ROSS-$\delta$-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $N + n$	 (upper bound) 					& 	      												\\ \hline
 SOC 					&$\mathcal{O}(N)$		&   $3N$									& Every CR node $i$ broadcasts channel availability on all cluster members, which is $|C(i)| |\mathcal{K}|$ bytes
 \\ \hline
 Centralized			&$\mathcal{O}(N)$			&	$N + n + m$ (upper bound) \cite{Efficient_broadcasting_gathering_adhoc}		& clustering result, which is 2$N$ bytes \tnotex{tnote:robots-r1} 					\\ \hline
\end{tabular}
    \begin{tablenotes}
      \item\label{tnote:robots-r1}Assuming the data structure of the clustering result is in the form of $\{i, C\}, i\in C, i\in \mathcal{N}$.
    \end{tablenotes}
    \end{threeparttable}
}
}
\hfill{}
\end{table*}
\end{center}
